\bf Hierarchical Forecasts Reconciliation

### 2019-07-02 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
More changes to writing

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  In \todo{references}, this matrix is written in the form $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases), where $\bm{G}$ is an $(n-m)\times n$ matrix.  This facilitates an interpretation of reconciliation as a two-step process, in the first step base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

	\subsection{Unbiasedness preserving property}

@@

	\subsection{Why do projections work?}

	Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

	Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$. Following subsections will explicitly discuss the different projection based reconciliation methods and their optimality based on distinct distance measures.

	\subsubsection{OLS reconciliation}

	Recall that in OLS reconciliation, $\bm{R}_\perp=\bm{S}$ and thus it orthogonally projects $\hat{\bm{y}}$ to the coherent subspace. Further, it minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$. In addition to that Figure \ref{fig:Schematic_OLSRecon} also shows that $\tilde{\bm{y}}$ is always closer to $\bm{y}$ than $\hat{\bm{y}}$ in terms of the Euclidean distance which is directly followed from the Pythagorean theorem. It also implies that the sum of squared error for OLS reconciled forecasts are always less than that for base forecasts.

	\clearpage		
	\begin{figure}[!ht]
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{
			\input{Figs/orth_pointforerec_schematic}
		}
		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$ }\label{fig:Schematic_OLSRecon}
	\end{figure}

	\subsubsection{MinT reconciliation}

	\subsubsection{Bottom-up method}

	Bottom-up method is one of the traditional and simplest ways of producing coherent forecasts. Under this approach, the incoherent forecasts are projected to the coherent subspace along the direction which is perpendicular to the bottom level series. In terms of distances, this method minimises the distance between reconciled and unreconciled forecasts only along the dimension corresponding to the bottom-level series. Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.

>>>>

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  One way to achieve this is with a matrix $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases), where $\bm{G}$ is an $(n-m)\times n$ matrix.  This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix.  We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.  This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011} where the connection between OLS and orthogonal projection should be clear.

	\subsection{Orthogonal projection}

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecast should be `close'.  The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the truth.

	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.  A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible given that $\tilde{\bm{y}}\in\mathfrak{s}$.  In this way reconciliation via orthogonal projection does not lead to large adjustments of the base forecasts.

	The second property introduced above has been the focus of theoretical results in the forecast reconciliation literature.  He we provide a more streamlined version of proofs by \cite{VanErven2015a} and \cite{Wickramasuriya2017} before providing geometrical intuition aimed at simplifying the reader's understanding of these proofs.

	Consider the Euclidean distance between a forecast and the target, which is equivalent to the root total squared error. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

	\todo{compare to van Erven and Wickremasuriya more explictly}

	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.  In this schematic, the coherent subspace is depicted as a black arrow.  The base forecast $\hat{\bm{y}}$ is shown as a blue dot.  Since it is incoherent it does not lie of $\mathfrak{s}$.  Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.  Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.

	\begin{figure}[H]
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
		\label{fig:Schematic_OLSRecon}
		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$}

	\end{figure}

	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle.  In this triangle the distance between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.  As such reconciliation is guaranteed to reduce the squared error of the forecast.

    The theorem is in some ways perhaps more powerful than perhaps previously understood.  The theorem is often stated in terms of expectations\todo{check other proofs}.  However, the distance reducing property result is stronger than that since it will hold for any realisation and any forecast.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.

    However, in other ways, the theorem is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts both for all realisations and in expectation, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

	\subsection{Oblique Projections}

	\section{The issue of bias}

@@
